Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-06-24 writing/DraftExposurePaper/DraftExposurePaper.Rmd
Added code for distance count plot/ rain count plot

@@

@@

>>>>

```{r echo = FALSE}
distance_exposure <- county_distance(counties = my_fips,
                                 start_year = 1988, end_year = 2011,
                                 dist_limit = 100)
distance_1000 <- distance_exposure %>%
        arrange(desc(storm_dist)) %>%
        group_by(fips) %>%
        summarise(value = n()) %>%
        rename(region = fips) %>%
        mutate(region = as.numeric(region), value = as.numeric(value)) %>%
        arrange(desc(value)) %>%
        slice(1:1000)
map_dist_1000 <- county_choropleth(distance_1000, 
                              title = "Hits by County\nfor Distance < 100 mm",
                              legend = "Hits per County", num_colors = 9,
                              state_zoom = eastern_states)
map_dist_1000 + scale_fill_brewer("Hits per\nCounty", palette = "YlGnBu", na.value = "white")
```

@@

```{r echo = FALSE}
distance_exposure <- county_distance(counties = my_fips,
                                 start_year = 1988, end_year = 2011,
                                 dist_limit = 100)
distance_1000 <- distance_exposure %>%
        arrange(desc(storm_dist)) %>%
        group_by(fips) %>%
        summarise(value = n()) %>%
        rename(region = fips) %>%
        mutate(region = as.numeric(region), value = as.numeric(value)) %>%
        arrange(desc(value))
map_dist_count <- county_choropleth(distance_1000, 
                              title = "Hits by County\nfor Distance < 100 mm",
                              legend = "Hits per County", num_colors = 9,
                              state_zoom = eastern_states)
map_dist_count + scale_fill_brewer("Hits per\nCounty", palette = "YlGnBu", na.value = "white")
```

@@

```{r echo = FALSE}
rain_count <- rain_exposure %>%
              group_by(fips) %>%
              summarise(count = n()) %>%
              rename(region = fips, value = count) %>%
              mutate(region = as.numeric(region), value = as.numeric(value))
map_counts <- county_choropleth(rain_count,
                                title = "Hits by County\nfor Rain > 75 mm",
                                legend = "Hits per County", num_colors = 9,
                                state_zoom = eastern_states)
map_counts + scale_fill_brewer("Hits per\nCounty", palette = "YlGnBu", na.value = "white")
```
